Towards a self-healing swarm through the removal of voids and anomalies

### 2018-10-09 paper.tex
More

\textit{Concave reduction} is a form of self-healing, it is a process that causes a swarm to coalesce towards a more geometrically stable shape. This is achieved by removing voids and concave edges. The technique defined in this paper functions without the need for inter-agent or global messaging. It is implemented at the local agent level through proximity detection.

@@

\section{Swarm Model}\label{sec:Swarm Model}
To describe the removal of voids a swarming model needs to be defined. Equation~\ref{eq:BotPhysics1} defines a weighted algorithm that includes cohesion, repulsion, direction and obstacle avoidance ($v_c(b), v_r(b), v_d(b), v_o(b)$). The weightings $k_c, k_r, k_d, k_o$ allow each component to be scaled thereby creating an adaptable swarming effect.

@@

\textit{Repulsion} $v_{r}(b)$, as defined in Equation~\ref{eq:Repulsion1} is the resultant directional movement required to prevent agents colliding where $rep(b)$ is a function that returns a set of agents that are within the agent $b$ repulsion range.

@@

\textit{Cohesion} $v_{c}(b)$, as defined in Equation~\ref{eq:FlyToCentre1} is the resultant movement that makes the agent move towards each other to form a cohesive structure where $nbr(b)$ is a function that returns set of all agents that are within agent $b$ cohesion range.

@@

\textit{Direction} $v_d(b)$, as shown in Equation~\ref{eq:Direction} is the directional vector for an agent. Where $d$ is the goal.

@@

Obstacles, like agents, can be represented as a point in the system. As an agent moves it may enter an obstacle's \textit{obstacle repulsion field} ($O_b$) causing the agent to move away. In this paper agents are modelled with a fixed \textit{obstacle repulsion field} ($O_b$). If an agent enters the field range a vector of magnitude $O_b$ is applied. If more than one obstacle is within the field effect, the applied repulsion vector is the sum of the repulsion vectors due to each obstacle~(Figure~\ref{fig:Obstacle1}). The result is normalised and scaled such that the magnitude is the same as the field distance~$O_b$ as shown in Equation~\ref{eq:Obstacle2}.

@@

Equation~\ref{eq:Obstacle2} shows the resultant repulsion vector $v_o(b)$ for an agent. $\{o~\in~O~:~\magn{ob}~\leq~O_b\}$ is the set of obstacles that are within range of agent $b$. $O$ is the set of obstacles. The obstacles are identified using the distance between an agent and an obstacle $\magn{ob}$ and comparing the result to the fixed obstacle repulsion range~$O_b$. The applied repulsion is calculated by scaling the normalised sum of the normalised vectors $\widehat{ob}$ by $O_b$. Note that $\string^$ is the equivalent of $\hat{v} = \frac{v}{\magn{v}}$ the normalised vector.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Images/moon.pdf}}]{Alun Moon}
  has been a Senior Lecturer at Northumbria University for 17 years. His first degree is in pure and applied mathematics (1973-4), his Masters in mathematics (mathematical logic, category theory, 1975), and he has a PhD in computer science (formal methods for distributed embedded systems, 2010) from Northumbria University. Before that Alun worked in teaching and the computing industry.
  \end{IEEEbiography}

>>>>

\textit{Concave reduction} is a form of self-healing, it is a process that creates a movement that makes a swarm coalesce towards a more geometrically stable shape. This is achieved by removing voids and concave edges. The techniques defined in this paper function without the need for inter-agent or global messaging using only local proximity detection.

@@

\section{Swarm Model}\label{sec:Swarm Model}
To describe the removal of voids a swarming model needs to be defined. Equation~\ref{eq:BotPhysics1} defines a weighted model that includes cohesion, repulsion, direction and obstacle avoidance ($v_c(b), v_r(b), v_d(b), v_o(b)$). The weightings $k_c, k_r, k_d, k_o$ allow each component to be scaled to tailor the swarming effect.

@@

\textit{Repulsion} $v_{r}(b)$, defined in Equation~\ref{eq:Repulsion1}, is the directional movement required to prevent agents colliding. $rep(b)$ is a function that returns a set of agents that are within an agent's $b$ repulsion range.

@@

\textit{Cohesion} $v_{c}(b)$, defined in Equation~\ref{eq:FlyToCentre1}, calculates the movement that makes an agent move towards other agents to form a cohesive structure. $nbr(b)$ is a function that returns a set of agents that are within an agent's ($b$) cohesion range.

@@

\textit{Direction} $v_d(b)$, defined in Equation~\ref{eq:Direction}, generates a directional vector for an agent to move towards a destination defined as $d$.

@@

Obstacles, like agents, can be represented as a point. As an agent moves it may enter an obstacle's \textit{repulsion field}. If this occurs then the agent should move away. In this paper agents are modelled with a fixed \textit{obstacle repulsion field} ($O_b$). If an agent enters the field a vector of magnitude $O_b$ is applied. If more than one obstacle is within the field, the applied repulsion vector is the sum of the repulsion vectors~(Figure~\ref{fig:Obstacle1}). The resultant vector is normalised and scaled such that the magnitude is the same as the field distance~$O_b$ as shown in Equation~\ref{eq:Obstacle2}.

@@

Equation~\ref{eq:Obstacle2} shows the repulsion vector $v_o(b)$ for an agent. $\{o~\in~O~:~\magn{ob}~\leq~O_b\}$ is the set of obstacles that are within the range of agent $b$. $O$ is the set of obstacles. The obstacles are identified using the distance between an agent and an obstacle $\magn{ob}$ and comparing the result to the fixed obstacle repulsion field~$O_b$. The applied repulsion is calculated by scaling the normalised sum of the normalised vectors $\widehat{ob}$ by $O_b$. Note that $\string^$ is the equivalent of $\hat{v} = \frac{v}{\magn{v}}$ the normalised vector.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Images/moon.pdf}}]{Alun Moon} has been a Senior Lecturer in Computing at Northumbria Universiy since 2001. He has a PhD from Newcastle University in Electronic Engineering, a MSc from Hull University in Mechatronics, a PgDip in Astronomical Technology from Edinburgh University, and a BEng in Materials Science from Liverpool University.
Prior experience as a research associate at Newcastle University included, embedded systems, engineering system modelling, and engineering visualisation.
\end{IEEEbiography}
